JMLR-14-133-4: Point-to-Point Reply

### 2015-01-05 pkg/partykit/inst/mloss/review4/p2p.tex
wrap-up
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@673 255f4249-2263-4417-b1ea-8498779e27a7

>>>>

Certainly, much more work can be done on general software for random forests
as well as improvements of the \texttt{cforest} function.  We intend to do
so in the future by tackling some of the open conceptual issues described in
our previous replies.  But, the current \texttt{partykit::cforest} function
clearly shows that also implementations of random forests will benefit from
the unified tree infrastructure established in the partykit package.
